Quasicharacters and the function-sheaf dictionary

### 2014-09-09 crelle-dictionary.tex
Corrected reference to EGA IV.

For any $n\leq m$,  the surjective ring homomorphism $R_{m} \to R_n$ determines a
natural transformation 
\[
\varrho^R_{n\leq m} : \Gr^R_{m} \to \Gr^R_n
\]
between additive functors.
Crucially, $\varrho^R_{n\leq m}(X): \Gr^R_{m}(X)\to \Gr^R_n(X)$ is an affine morphism of $\Fq$-schemes, for every $R$-scheme $X$ and every $n\leq m$ \cite{bertrapelle-gonzales:Greenberg}*{Prop 4.3}.
This observation is key to the proof that, for any scheme $X$ over $R$, the projective limit 
\[
\Gr_R(X) \ceq \varprojlim_{n\in \NN} \Gr^R_n(X),
\]
taken with respect to the surjective morphisms $\varrho^R_{n\leq m}(X) : \Gr^R_{m}(X) \to \Gr^R_n(X)$,
exists in the category of group schemes over $\Fq$;
see \cite{EGAIV3}*{\S 8.13}.
This leads to the definition of what we shall call the {\it Greenberg transform}:
\[
\Gr_R : \Sch{R} \to \Sch{\Fq}.
\]
By construction, the $\Fq$-scheme $\Gr_R(X)$ comes equipped with morphisms 
\[
\varrho^R_n(X) : \Gr^R(X) \to \Gr^R_n(X),\qquad \forall n\in \NN.
\]

>>>>

For any $n\leq m$,  the surjective ring homomorphism $R_{m} \to R_n$ determines a
natural transformation 
\[
\varrho^R_{n\leq m} : \Gr^R_{m} \to \Gr^R_n
\]
between additive functors.
Crucially, $\varrho^R_{n\leq m}(X): \Gr^R_{m}(X)\to \Gr^R_n(X)$ is an affine morphism of $\Fq$-schemes, for every $R$-scheme $X$ and every $n\leq m$ \cite{bertrapelle-gonzales:Greenberg}*{Prop 4.3}.
This observation is key to the proof that, for any scheme $X$ over $R$, the projective limit 
\[
\Gr_R(X) \ceq \varprojlim_{n\in \NN} \Gr^R_n(X),
\]
taken with respect to the surjective morphisms $\varrho^R_{n\leq m}(X) : \Gr^R_{m}(X) \to \Gr^R_n(X)$,
exists in the category of group schemes over $\Fq$;
see \cite{EGAIV3}*{\S 8.2}.
This leads to the definition of what we shall call the {\it Greenberg transform}:
\[
\Gr_R : \Sch{R} \to \Sch{\Fq}.
\]
By construction, the $\Fq$-scheme $\Gr_R(X)$ comes equipped with morphisms 
\[
\varrho^R_n(X) : \Gr^R(X) \to \Gr^R_n(X),\qquad \forall n\in \NN.
\]
